### 2019-03-27 _publications/jors/paper.tex
Changes for @tonkmr

\section*{Title}
\par\bigskip
PFHub: The Phase-Field Community Hub\\[\baselineskip]
\url{https://pages.nist.gov/pfhub}

@@

Scientific communities struggle with the challenge of effectively and
efficiently sharing content and data. An online portal provides a
valuable space for scientific communities to discuss challenges and
collate scientific results. Examples of such portals include the
Micromagenetic Modeling Group ($\mu$MAG~\cite{mumag}), the Iteratomic
Potentials Repository (IPR~\cite{ipr1, ipr2}) and on a larger scale
the NIH Genetic Sequence Database (GenBank~\cite{genbank}). In this
work, we present a description of a generic web portal that leverages
existing online services to provide a framework that may be adopted by
other scientific communities. The first deployment of the PFHub
framework supports phase-field practitioners and code developers
participating in an effort to improve quality assurance for
phase-field codes.

@@

Small scientific communities do not often have the resources to build
and host dedicated web infrastructure to support their varied content
and data requirements. In particular, hosting and supporting a complex
content management system (CMS) including web servers, web frameworks
and databases requires a great deal of configuration and long term
support and funding. Furthermore, a turnkey CMS solution may not meet
requirements for a particular scientific group that may require arcane
data formats, unusual data display and custom client-side automation.
The PFHub effort, instead of focusing on the CMS tool, focuses on
customizing and delivering the "client-side" requirements whilst
delegating back-end functionality to external services and then
integrate with those services' APIs. The PFHub current effort supports
a community of phase field code developers.

\section*{Introduction (old)}

The phase-field method (PFM) describes material interfaces at the
mesoscopic scale between atomic scale models and macroscale models.
The PFM is well established and there are an assortment of code
frameworks (\emph{e.g.}, MOOSE~\cite{moose},
PRISMS-PF~\cite{prisms-pf}, FiPy~\cite{fipy},
MMSP~\cite{mmsp}) available for
solving the wide variety of mesoscale phenomena (\emph{e.g.},
dendritic growth, spinodal decomposition, grain growth). However,
phase-field research groups often develop codes in isolation and do
not support or distribute the code bases to the wider community. PFHub
is a community effort spearheaded by the Center for Hierarchical
Materials Design at Northwestern University and the National Institute
of Standards and Technology to support the development of phase-field
codes. In particular, the PFHub effort focuses on improving
cross-collaboration between phase-field code developers and
practitioners by providing a standardized set of benchmark
problems~\cite{bm1, bm2} along with a web framework for uploading and
comparing benchmark results from different codes.

@@

The PFHub website provides a facility for uploading, displaying and
comparing results from the benchmark problems. The website uses the
Jekyll static website generator~\cite{jekyll} along with automated
frontend processing to eliminate the need for content management
systems~\cite{cmsfree}, which are generally costly to maintain
especially for small scientific communities with limited funding and
staffing.

>>>>

\section*{Title}
\par\bigskip
PFHub: The Phase-Field Community Hub\\[\baselineskip]

@@

Scientific communities struggle with the challenge of effectively and
efficiently sharing content and data. An online portal provides a
valuable space for scientific communities to discuss challenges and
collate scientific results. Examples of such portals include the
Micromagenetic Modeling Group ($\mu$MAG~\cite{mumag}), the Iteratomic
Potentials Repository (IPR~\cite{ipr1, ipr2}) and on a larger scale
the NIH Genetic Sequence Database (GenBank~\cite{genbank}). In this
work, we present a description of a generic web portal that leverages
existing online services to provide a framework that may be adopted by
other small scientific communities. The first deployment of the PFHub
framework supports phase-field practitioners and code developers
participating in an effort to improve quality assurance for
phase-field codes.

@@

Generally, small scientific communities do not have the resources to
build and host dedicated web infrastructure to support their varied
content and data requirements. In particular, hosting and supporting a
complex content management system (CMS) including web servers, web
frameworks and databases requires a great deal of configuration and
long term support and funding. Furthermore, a turnkey CMS solution may
not meet requirements for a particular scientific group that may
require arcane data formats, custom data displays and client-side
automation. The PFHub effort, instead of focusing on the CMS tool,
focuses on customizing and delivering the "client-side" requirements
whilst delegating back-end functionality to external services that
provide dependable APIs~\cite{cmsfree}.

PFHub is a community effort spearheaded by the Center for Hierarchical
Materials Design at Northwestern University and the National Institute
of Standards and Technology in support of phase-field code
development. The current PFHub deployment~\cite{pfhub} focuses on
improving cross-collaboration between phase-field code developers and
practitioners by providing a standardized set of benchmark
problems~\cite{bm1, bm2} and a workflow for uploading and comparing
benchmark results from different phase-field codes (\emph{e.g.},
MOOSE~\cite{moose}, PRISMS-PF~\cite{prisms-pf}, FiPy~\cite{fipy},
MMSP~\cite{mmsp}).

This paper presents the first deployment of the PFHub framework
including its ``client-side'' focused design, how it employs external
services and meta-data about the code base.

@@

The PFHub website provides a facility for uploading, displaying and
comparing results from the benchmark problems. The website uses the
Jekyll static website generator~\cite{jekyll} along with automated
front-end processing to eliminate the need for a CMS~\cite{cmsfree},
which are generally costly to maintain especially for small scientific
communities with limited funding and staffing.
